Supplementary material

### 2021-12-09 submission/manuscript.rmd
add model selections and rmse for high effects to supplement

```{r adaptive, echo=FALSE, warning=FALSE, message=FALSE}
adaptiveSelections <- readr::read_csv(here::here("data/processed/adaptiveSelections.csv"))
rmseDistribution <- readr::read_csv(here::here("data/processed/rmseDistribution.csv"))
aucDistribution <- readr::read_csv(here::here("data/processed/discriminationDistribution.csv"))
```
The linear interaction model outperformed all RCS methods in terms of
RMSE in scenarios with true constant relative treatment effect (OR =
0.8, N = `r 4250` and AUC = 0.75), strong linear and even strong
quadratic deviations from a constant relative treatment effect
(Figure \ref{fig:rmsebase}; panels A-C). However, with
non-monotonic deviations from a constant relative treatment effect,
the RMSE of the linear interaction model increased substantially, 
especially in the presence of treatment-related harms (Figure 
\ref{fig:rmsebase}; panel D). In these scenarios, RCS-3 outperformed all other
methods in terms of RMSE. The constant treatment effect
approach had overall best performance under true constant treatment
effect settings, but was sensitive to all considered deviations,
resulting in increased RMSE. Finally, the adaptive approach had
comparable performance to the best-performing method in each
scenario. However, in comparison with the best-performing approach, its RMSE was
more variable across the 1000 replications in the scenarios with linear and
non-monotonic deviations, especially when also including moderate or strong
treatment-related harms. This is caused by wrongly selecting the constant
treatment effect model in a substantial proportion of the replications
(Supplement, Table XX).

@@

```{r gusto, cache=TRUE, echo=FALSE, fig.cap="Individualized absolute benefit predictions based on baseline risk when using a constant treatment effect approach, a linear interaction approach and RCS smoothing using 3,4 and 5 knots. Risk stratified estimates of absolute benefit are presented within quartiles of baseline risk as reference.", fig.show="hold", out.width = '100%'}
knitr::include_graphics(here::here("figures/gusto.png"))
```

>>>>

```{r adaptive, echo=FALSE, warning=FALSE, message=FALSE}
adaptiveSelections <- readr::read_csv(here::here("data/processed/adaptiveSelections.csv"))
rmseDistribution <- readr::read_csv(here::here("data/processed/rmseDistribution.csv"))
aucDistribution <- readr::read_csv(here::here("data/processed/discriminationDistribution.csv"))
```
The linear interaction model outperformed all RCS methods in terms of
RMSE in scenarios with true constant relative treatment effect (OR =
0.8, N = `r 4250` and AUC = 0.75), strong linear and even strong
quadratic deviations from a constant relative treatment effect
(Figure \ref{fig:rmsebase}; panels A-C). However, with
non-monotonic deviations from a constant relative treatment effect,
the RMSE of the linear interaction model increased substantially, 
especially in the presence of treatment-related harms (Figure 
\ref{fig:rmsebase}; panel D). In these scenarios, RCS-3 outperformed all other
methods in terms of RMSE. The constant treatment effect
approach had overall best performance under true constant treatment
effect settings, but was sensitive to all considered deviations,
resulting in increased RMSE. Finally, the adaptive approach had
comparable performance to the best-performing method in each
scenario. However, in comparison with the best-performing approach, its RMSE was
more variable across the 500 replications in the scenarios with linear and
non-monotonic deviations, especially when also including moderate or strong
treatment-related harms. This is caused by wrongly selecting the constant
treatment effect model in a substantial proportion of the replications
(Supplement, Figure S3).

@@

```{r gusto, cache=TRUE, echo=FALSE, fig.cap="Individualized absolute benefit predictions based on baseline risk when using a constant treatment effect approach, a linear interaction approach and RCS smoothing using 3,4 and 5 knots. Risk stratified estimates of absolute benefit are presented within quartiles of baseline risk as reference.", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/gusto.tiff")))
# knitr::include_graphics(here::here("figures/gusto.png"))
```

### 2021-12-09 submission/manuscript.tex
add model selections and rmse for high effects to supplement

\begin{figure}
\includegraphics[width=1\linewidth]{/home/arekkas/Documents/Projects/arekkas_HteSimulation_XXXX_2021/figures/gusto} \caption{Individualized absolute benefit predictions based on baseline risk when using a constant treatment effect approach, a linear interaction approach and RCS smoothing using 3,4 and 5 knots. Risk stratified estimates of absolute benefit are presented within quartiles of baseline risk as reference.}\label{fig:gusto}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/gusto-1} \caption{Individualized absolute benefit predictions based on baseline risk when using a constant treatment effect approach, a linear interaction approach and RCS smoothing using 3,4 and 5 knots. Risk stratified estimates of absolute benefit are presented within quartiles of baseline risk as reference.}\label{fig:gusto}
\end{figure}

### 2021-12-09 submission/supplement.rmd
add model selections and rmse for high effects to supplement

```{r tab1, echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE}
 asd <- read_csv(
  here("data/processed/analysisIds.csv")
) %>%
  select(-"type")
kableExtra::kable(
  asd,
  format = "latex",
  escape = FALSE,
  longtable   = TRUE,
  align       = "r",
  booktabs    = TRUE,
  caption     = "",
  col.names   = c(
    "Scenario",
    "Base",
    "N",
    "AUC",
    "Treatment-related harm",
    paste0("b", 0:8),
    paste0("g", 0:2),
    "c",
    "Average benefit"
  ),
  digits      = 2,
  format.args = list(
    big.mar      = ",",
    decimal.mark = "."
  )
) %>%
  kableExtra::landscape() %>%
  kableExtra::add_header_above(
    c(
      "Analysis ID"           = 5,
      "Baseline risk"         = 9,
      "True treatment effect" = 4
      )
  ) %>%
  kableExtra::kable_styling(font_size = 7)
```

>>>>

```{r tab1, echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE}
 asd <- read_csv(
  here("data/processed/analysisIds.csv")
) %>%
  select(-"type")
kableExtra::kbl(
  asd,
  format = "latex",
  escape = FALSE,
  longtable   = TRUE,
  align       = "r",
  booktabs    = TRUE,
  caption     = "",
  col.names   = c(
    "Scenario",
    "Base",
    "N",
    "AUC",
    "Treatment-related harm",
    paste0("b", 0:8),
    paste0("g", 0:2),
    "c",
    "Before harms",
    "After harms"
  ),
  linesep = c('', '', '', '\\addlinespace'),
  digits      = 2,
  format.args = list(
    big.mar      = ",",
    decimal.mark = "."
  )
) %>%
  kableExtra::landscape() %>%
  kableExtra::add_header_above(
    c(
      "Analysis ID"           = 5,
      "Baseline risk"         = 9,
      "True treatment effect" = 4,
      "Benefit"               = 2
      )
  ) %>%
  kableExtra::kable_styling(font_size = 7)
```

\newpage
\begin{landscape}
```{r adaptiveBase, cache=FALSE, echo=FALSE, fig.cap="Adaptive model selection rates for the base case scenario true prediction AUC of 0.75, sample size of 4250", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/selected_model_adaptive_base.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```
\end{landscape}

\newpage
\begin{landscape}
```{r adaptiveSampleSize, cache=FALSE, echo=FALSE, fig.cap="Adaptive model selection rates for sample size of 17000.", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/selected_model_adaptive_sample_size.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```
\end{landscape}

\newpage
\begin{landscape}
```{r adaptiveAuc, cache=FALSE, echo=FALSE, fig.cap="Adaptive model selection rates for true prediction AUC of 0.85.", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/selected_model_adaptive_auc.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```
\end{landscape}

\newpage
```{r rmseHighBase, cache=FALSE, echo=FALSE, fig.cap="RMSE high effect base", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/rmse_high_base.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

\newpage
```{r rmseHighSampleSize, cache=FALSE, echo=FALSE, fig.cap="RMSE high effect sample size", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/rmse_high_sample_size.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```

\newpage
```{r rmseHighAuc, cache=FALSE, echo=FALSE, fig.cap="RMSE high effect auc", fig.show="hold", out.width = '100%'}
grid::grid.raster(tiff::readTIFF(here("figures/rmse_high_auc.tiff")))
# knitr::include_graphics(here::here("figures/calibration_base.png"))
```
